Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-04-15 article.tex
No need to repeat what the alignment params are, thanks @Giappo

\subsection{pirouette's pipeline}

@@

The first step in \verb;pirouette; is to simulate a DNA alignment from the 
given phylogeny. 
To do so, we must specify an alignment model $\mathit{A}$ which consists of a 
DNA root sequence $\mathit{r_{s}}$, a DNA mutation rate $\mathit{m_{r}}$, a
site model $\mathit{s_{m}}$ (in this context: a nucleotide substitution model \giovanni{We already specified this in 2.1, when explaining the first step. Do we need to repeat it?}) 
and a clock model $\mathit{c_{m}}$. 
In this example, the DNA root sequence consists in four blocks of 250 
mononucleotides each, 
where the per-nucleotide mutation rate is 0.1 mutations per unit time.
We use a Jukes-Cantor (JC, \cite{jukes1969evolution}) site model
and a strict clock model as these are the simplest.
A JC site model
assumes that mutation rates between nucleotides are equal and constant. 
A strict clock model assumes that the mutation rates 
of all species are equal and constant.

>>>>

\subsection{pirouette's pipeline}\label{subsec:pipeline}

@@

The first step in \verb;pirouette; is to simulate a DNA alignment from the 
given phylogeny, as described in subsection~\ref{subsec:pipeline}.
In this example, the DNA root sequence $\mathit{r_{s}}$ 
consists in four blocks of 250 
mononucleotides each, 
where the per-nucleotide mutation rate $\mathit{m_{r}}$ 
is 0.1 mutations per unit time.
We use a Jukes-Cantor (JC, \cite{jukes1969evolution}) site model
and a strict clock model as these are the simplest.
A JC site model
assumes that mutation rates between nucleotides are equal and constant. 
A strict clock model assumes that the mutation rates 
of all species are equal and constant.
